The eclipse of the V773 Tau B circumbinary disk

### 2022-07-12 src/tex/ms.tex
added Dario 2,9,10
added zenodo sandbox and figure 3
added fig 8

\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\logg}{\ensuremath{\log g}}
\newcommand{\Msun}{$M_{\odot}$}
\newcommand{\logl}{log($L/L_{\odot}$)}
\def\kms{\ifmmode{\rm km\th s^{-1}}\else km\th s$^{-1}$\fi}
\def\th{\thinspace}

\newcommand\todo[1]{\colorbox{yellow}{\textcolor{red}{#1}}}

@@

\begin{figure*}
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/v773tau_fig1.pdf}
    \caption{Optical photometry of the V773 Tau system.
    %
    The four different photometric surveys are represented by different colours, and each photometric series has been normalised using flux outside the main eclipse.
    %
    The inset panel shows the eclipse light curve in greater detail.
    %
    The PTF and KELT curves show different depths of the eclipse, indicating the presence of sub-micron dust that causes different amounts of optical extinction in the different pass bands of the two surveys.}
\label{fig:lc}
\end{center}
\end{figure*}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/V773Tau-nocoro.pdf}
    \caption{SPHERE image of V773 Tau AB and C. The axes are centred on A, and B is not visible in this image, being under the first diffraction ring of the A component.
    %
    C is shown to the lower left of AB.
    %
    North is up and East to the left.}
    \label{fig:sphere}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/lsc_mcmc_tess.pdf}
    \caption{V773 Tau light curve as observed with TESS shown in the upper panel with brown dots.
    %
    The Stellar Variability models computed with Lomb-Scargle (blue) and MCMC (green) are overlapped and the residuals are indicated as a color scale.}
\label{fig:tess_variability}
\end{center}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/v773tau_fig_periodogram.pdf}
    \caption{Lomb-Scargle Periodograms for the merged photometry (top) and TESS (bottom), the periods with the highest powers are highlighted.}
    \label{fig:two_periodograms}
\end{figure}

@@

%
\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/longperiod_periodogram.pdf}
    \caption{Lomb-Scargle Periodograms for the two bands of ASAS-SN and KELT.
    %
    In grey (green) the periodogram before (after) removing the short-term rotational frequencies.
    %
    A peak at $\sim 68$ days is highlighted for the three datasets.}
    \label{fig:long_periodogram}
\end{figure}

>>>>

\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\logg}{\ensuremath{\log g}}
\newcommand{\Msun}{$M_{\odot}$}
\newcommand{\logl}{log($L/L_{\odot}$)}
\def\th{\thinspace}
\def\kms{\ifmmode{\rm km\th s^{-1}}\else km\th s$^{-1}$\fi}

@@

\begin{figure*}
\begin{center}
    \centering
%    \includegraphics[width=\textwidth]{figures/v773tau_fig1.pdf}
    \includegraphics[width=\textwidth]{figures/fig2_full_lightcurve.pdf}
    \caption{Optical photometry of the V773 Tau system.
    %
    The four different photometric surveys are represented by different colours, and each photometric series has been normalised using flux outside the main eclipse.
    %
    The inset panel shows the eclipse light curve in greater detail.
    %
    The PTF and KELT curves show different depths of the eclipse, indicating the presence of sub-micron dust that causes different amounts of optical extinction in the different pass bands of the two surveys.}
  \label{fig:lc}
  \script{fig2_complete_lightcurve.py}
\end{center}
\end{figure*}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/fig3_v773tau.pdf}
    \caption{SPHERE image of V773 Tau AB and C. The axes are centred on A, and B is not visible in this image, being under the first diffraction ring of the A component.
    %
    C is shown to the lower left of AB.
    %
    North is up and East to the left.}
  \label{fig:sphere}
  \script{make_fig3_v773tau.py}
\end{figure}

@@

\begin{figure}
\begin{center}
    \centering
    \includegraphics[width=\columnwidth]{figures/fig8_tess_stellar_var.pdf}
    \caption{V773 Tau light curve as observed with TESS shown in the upper panel with brown dots.
    %
    The Stellar Variability models computed with Lomb-Scargle (blue) and MCMC (green) are overlapped and the residuals are indicated as a color scale.}
  \label{fig:tess_variability}
  \script{fig8_tess_mcmc.py}
\end{center}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/fig9_periodograms.pdf}
    \caption{Lomb-Scargle Periodograms for the merged photometry (top) and TESS (bottom), the periods with the highest powers are highlighted.}
    \label{fig:two_periodograms}
    \script{fig9_periodograms.py}
\end{figure}

@@

%
\begin{figure}[ht]
    \centering
%    \includegraphics[width=\columnwidth]{figures/longperiod_periodogram.pdf}
    \includegraphics[width=\columnwidth]{figures/fig10_longperiod_periodogram.pdf}
    \caption{Lomb-Scargle Periodograms for the two bands of ASAS-SN and KELT.
    %
    In grey (green) the periodogram before (after) removing the short-term rotational frequencies.
    %
    A peak at $\sim 68$ days is highlighted for the three datasets.}
  \label{fig:long_periodogram}
  \script{fig10_long_periods.py}
\end{figure}
